### 2012-08-09 inst/examples/Reed.Rmd
replace deterministic with tiny growth noise
policycosts examples

``` {r  echo=FALSE, cache=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
orig = getOption("device")
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

@@

``` {r }
f <- BevHolt 
````

With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.005`.

``` {r }
pars <- c(A, B)
K <- (A-1)/B
````

@@

``` {r }
xmin <- 0
xmax <- 1.5 * K
grid_n <- 100
````

@@

``` {r noise}
z_g <- function() rlnorm(1,0, sigma_g)  # 1+(2*runif(1, 0,  1)-1) * sigma_g
````

@@

``` {r  SDP_Mat}
pdfn <- function(P, s){
  # dunif(P, 1 - s, 1 + s)
  dlnorm(P, 0, s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

@@

``` {r  }
SDP_Mat2 <- determine_SDP_matrix(f, pars, x_grid, h_grid, 0.01, pdfn)
````

@@

``` {r biblio, echo=FALSE, results="asis"}
knitcitations::bibliography("html")
````

>>>>

``` {r  echo=FALSE, cache=FALSE}
#opts_knit$set(upload.fun = socialR::flickr.url)
#options(device = function(width = 5, height = 5) {
#    pdf(NULL, width = width, height = height)
#})
knitcitations::cleanbib()
````

@@

``` {r }
f <- function (x, h, p) 
{
 sapply(x, function(x){
  	S = max(x - h, 0)
  	p[1] * S * (1 - S/p[2]) + S
  })
}

````

With parameters `K` = `r K <- 100` and `r` = `r r <- 1`.

``` {r }
pars <- c(r, K)
````

@@

``` {r }
xmin <- 0
xmax <- K
grid_n <- 200
````

@@

``` {r noise}
#z_g <- function() 1 + rlnorm(1,0, sigma_g)  
z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
````

@@

``` {r  SDP_Mat}
pdfn <- function(P, s){
   dunif(P, 1 - s, 1 + s)
#  dlnorm(P, 0, s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

@@

``` {r  }
SDP_Mat2 <- determine_SDP_matrix(f, pars, x_grid, h_grid, 0.001, pdfn)
````

@@

``` {r biblio, echo=FALSE, results="asis"}
# knitcitations::bibliography("html")
````

### 2012-08-09 inst/examples/policycosts/L1.Rmd
policycosts examples

>>>>

##

Plot the policy function and value function at certain values of previous harvest

``` {r policyfn_plot}
require(reshape2)
policies <- melt(data.frame(stock=x_grid, S = x_grid[opt$D[,1]], D = x_grid[det$D[,1]]), id="stock")
q1 <- ggplot(policies, aes(stock, stock - value, color=variable)) + geom_point() + xlab("stock size") + ylab("escapement") 
q1
````

and the value function (at equilibrium):

``` {r valuefn_plot}
q2 <- qplot(x_grid, opt$V, xlab="stock size", ylab="value") + 
geom_vline(xintercept=opt$S)
q2
````
